---
title: "Running with a control file"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running with a control file}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shellfishrisks)

load_shellfish()

batch <- "ctrl_demo_2"
```

First, we'll generate a control file with the default settings. This copies a .csv file named in this case "ctrl_file.csv" to your working directory. You could then open that file up and modify as you see fit. 

```{r}
ctrl_file_path <- generate_ctrl_file("ctrl_file")
```

We'll then run the `shellfishrisk` model using the settings in that control file. This will store the results in a folder called "results/{batch}". A copy of the control file used to create that run will be stored in "results/{batch}" as well. 

```{r, eval = TRUE}
run_shellfishrisk_ctrlfile(batch = batch, reps = 1, ctrl_file_path = ctrl_file_path)
```

And from there we can load and plot our results same as always.

```{r}
results <- serve_shellfish(batches = batch) # read the results stored in .txt files into a list object

results$survival

plot_shellfish(results, type = "rvars")

plot_shellfish(results, type = "fst")

plot_shellfish(results, type = "popsize")


```
